|

### 2020-05-08 paper/Manuscript.Rmd
Various bug fixes

author: 
  - name          : "Caspar J. van Lissa"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email         : "c.j.vanlissa@uu.nl"
  - name          : "Andreas M. Brandmaier"
    affiliation   : "3,4"
  - name          : "Loek Brinkman"
    affiliation   : "2,5"

affiliation:
  - id            : "1"
    institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"
  - id            : "3"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "4"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id            : "5"
    institution   : "UMC Utrecht"

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

>>>>

author: #"`r source('authors_yaml.R')`"
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
  - name: "Loek Brinkman"
    institution: "2,5"
  - name: "Aaron Peikert"
    institution: "6"
  - name: "Barbara Vreede"
    institution: "7"

affiliation: #"`r source('affiliation_yaml.R')`"
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "UMC Utrecht"
  - id: "6"
    institution: "Test"
  - id: "7"
    institution: "University Library Utrecht"

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).
